---
title: "p8105_hw1_cx2227"
author: "Chuyue Xiang"
date: 2019-09-17
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
```

# Problem 1

```{r problem_1}
p1_df = tibble(
  norm_samp = rnorm(8),
  norm_samp_pos = norm_samp > 0,
  vec_char = c ("1", "2", "3", "4", "5", "6", "7", "8"),
  vec_factor = factor(c("A", "A", "A", "B", "B", "B", "C", "C"))
)

mean(pull(p1_df, norm_samp))
mean(pull(p1_df, norm_samp_pos))
mean(pull(p1_df, vec_char))
mean(pull(p1_df, vec_factor))

```
It only worked when taking the mean of "norm_samp" and "norm_samp_pos" and did not work when taking the mean of "vec_char" and "vec_factor".


## Converting variables from one type to another

```{r problem1_part2, warning=FALSE}

### convert the logical vector to numeric, and multiply the random sample by the result
as.numeric(pull(p1_df, norm_samp_pos)) * pull(p1_df, norm_samp)

### convert the logical vector to a factor, and multiply the random sample by the result
as.factor(pull(p1_df, norm_samp_pos)) * pull(p1_df, norm_samp)

### convert the logical vector to a factor and then convert the result to numeric, and multiply the random sample by the result
as.numeric(as.factor(pull(p1_df, norm_samp_pos))) * pull(p1_df, norm_samp)
```

# Problem 2 

```{r}
p2_df = tibble(
  x = rnorm(500),
  y = rnorm(500),
  norm_samp_pos1 = x + y > 1,
  num_vec = as.numeric (norm_samp_pos1),
  fac_vec = as.factor (norm_samp_pos1)
)
```

## Short Description
- the number of row in `p2_df` is `r nrow(p2_df)` ;
- the number of column in `p2_df` is `r ncol(p2_df)` ;
- the mean of x is `r mean(pull( p2_df, x))` ; 
- the median of x is `r median (pull(p2_df, x))` ;
- the standard deviation of x is `r sd(pull ( p2_df, x))` ;
- the proportion of cases for which x + y > 1 is `r mean(pull(p2_df, norm_samp_pos1))`

## Scatterplot
```{r}
# Scatterplot for logical vector
ggplot(p2_df, aes( x = x, y = y, color = norm_samp_pos1)) + geom_point()

# Scatterplot for numeric vector
ggplot(p2_df, aes( x = x, y = y, color = num_vec)) + geom_point()

# Scatterplot for factor vector
ggplot(p2_df, aes( x = x, y = y, color = fac_vec)) + geom_point()

```











